Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it has to be refactored. Because of this, we will first look at where clones can be found. Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized. Apart from that, we will look at different \todo[inline]{make sure to explain that this is a different set of different types, because splitting clones by location in code is also a way to have different types} types of clones. A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone. We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match. We conduct our research on a large corpus of open source projects. We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}. However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \footnote{Scorpio is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs.}. We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). This is displayed in figure \ref{fig:clonerefactor}.

>>>>

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it has to be refactored. Because of this, we will first look at where clones can be found. Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized. A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone. We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match. We conduct our research on a large corpus of open source projects. We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}. However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}. However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements. We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically). This is displayed in figure \ref{fig:clonerefactor}.
